---
title: "R_learning"
author: "Nina"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Intro

This is the a R notebook for the most basic R.

```{r test}
library("palmerpenguins")
summary(penguins)
```

```{r check installed packages, results = "hide"}
 installed.packages() 
```


```{r}
install.packages("ggplot2")
library("ggplot2")
```

```{r find packages, eval=FALSE}
 find.package("tidyverse")
```

```{r, , results = "hide"}
install.packages("tidyverse")
```

```{r}
a<-1 # global environment
b<-2
c<-1
print(a) 
```
```{r}
ls() #a list of variables
```

```{r}
(-b + sqrt(b^2 - 2*a*c)) / (2*a)
```
如果 \(a^x = N\) (其中 \(a > 0\) 且 \(a \ne 1\))，则 \(x\) 叫做以 \(a\) 为底 \(N\) 的对数，记做 \(x = \log_a N\)。

The logarithm of \(N\) with base \(a\) is:
$$
\log_a N
$$
```{r}
?log #or ("log")
```


```{r}
args(log)
```
The base of the function log defaults to base=exp(1), means default base is exp(1).
```{r}

```

```{r}
log(8, base=2) # change default base to 2
```
```{r}
log(8,2) 
```

## Functions
```{r}
log(a)
```
### nested functions
```{r}
log(exp(a)) #nested
```
Functions are not the only pre-built objects in R, there are also data sets included for users to practice and test out functions
```{r}
data() #these data sets are objects that you can use by simply tying the names
```

```{r}
CO2
```

```{r}
pi
```
## Variable names
Make your codes readable, have to start with a letter, and they cannot contain spaces. 
Comments is very nice 
```{r}
## code to compute solution to quadratic
## equation of the form ax^2 + bx + c
## define the variables
a<- 2
b<- -1
c<- -4

## Now compute the solution
(-b + sqrt(b^2-4*a*c))/2*a
```

## Practice


```{r}
a <- 2
b <- -1
c <- -4

# Calculate the discriminant
discriminant <- b^2 - 4 * a * c

# Calculate the two solutions
x1 <- (-b + sqrt(discriminant)) / (2 * a)
x2 <- (-b - sqrt(discriminant)) / (2 * a)

# Print the solutions with 3 significant digits
cat("The solutions are:", signif(x1, 3), "and", signif(x2, 3), "\n")
```

```{r}
log(1024, base=4)
```
## Create data frame
```{r}
temp <- c(35, 88, 42, 84, 81, 30)
city <- c("Beijing", "Lagos", "Paris", "Rio de Janeiro", "San Juan", "Toronto")
city_temps <- data.frame(name = city, temperature = temp)
View(city_temps)
```



