---
title: "R Notebook"
output: html_notebook
---
## varibles types
```{r}
a<- 2
class(a)
```
```{r}
class(ls)
```
## Data Frames (Tables)
```{r}
install.packages("dslabs")
library(dslabs)
data("murders") #the data is stored in the object murders
```

```{r}
class(murders) 
```
```{r}
str(murders) 
```
Note: 51 observations, means 51 rows and 5 variables: state, abb(abbreviation), region, population, total
```{r}
head(murders)
```
$- called the Accessor

```{r}
murders$population
```
51 Vectors
```{r}
pop<- murders$population
length(pop)
class(pop)
```

```{r}
mes(murders)
```
Use quotes to distinguish between variable names and character strings
```{r}
"a" #character string
```
```{r}
class(murders$state)
```
Another type of vector: logical vectors
TRUE or FALSE
```{r}
Z<- 3 < 2
Z
class(Z)
```
One more data type: 

```{r}
class(murders$region)
```
Note: Categorical Data

```{r}
levels(murders$region)
```
Note: Saving categorical data is more memory efficient, in fact, we store the levels as integers.
IT CAN BE EASILY BE CONFUSED WITH CHARACTERS!

## Practice
```{r}
library(dslabs)
data(movielens)
str(movielens)
```
```{r}
class(movielens$title)
```
```{r}
class(movielens$genres)
levels(movielens$genres)
nlevels(movielens$genres)
```


