---
title: "Vectors"
output: html_notebook
---

## Creating vectors
A vector is a series of values, all of the same type. 
```{r}
codes <- c(380, 124, 818) #c stands for concatenate
country <- c("Italy" , "Canada", "Egypt" )
class(codes)
```
Connecting Numeric and Character Vectors
```{r}
codes <- c("Italy"=380, "Canada"=124, "Egypt"=818)
codes
class(codes)
```
```{r}
class(3L) #class(3) is numeric, but class(3L) is integer
3L-3
```
```{r}
a<- seq(1, 10)
class(a)
```
Note: integer and numeric are difficult to distinguish, though intergers take less memory.
```{r}
codes <- c(380, 124, 818) 
country <- c("Italy" , "Canada", "Egypt" )
names(codes) #NULL
names(codes)<- country 
codes
names(codes)
```
```{r}
?"names"
```

```{r}
v <- c(a = 1, b = 2, c = 3)
names(v)
```


```{r}
seq(1,10)
seq(1, 10, 2)
1:10
```

## Subsetting

```{r}
codes[2]
codes[c(1,3)]
codes[1:2]
codes["Canada"]
codes[380]
codes[c("Egypt", "Italy")]
```
## Vector coercion
```{r}
x <- c(1, "Canada", 3)
x
```
Note: it changes all numbers into characters.
```{r}
x<- 1:5
y<- as.character(x)
y
as.numeric(y)
```
We can avoid coercion in R, by changing characters to numeric or vice-versa.
```{r}
x <- c(1, 3, 5,"a")
class(x)
x<- as.numeric(x)
x
class(x)

```

## Missing data
```{r}
x<- c("1","b","3")
as.numeric(x)
```
## Remove NA
```{r}
# Create the ind vector
library(dslabs)
data(_example)
ind <- is.na(na_example)

# We saw that this gives an NA
mean(na_example)

# Compute the average, for entries of na_example that are not NA 
mean(na_example[!ind])
```

```{r}
library(NHANES)
data(NHANES) 
summarize(NHANES, Weight= mean(Weight, na.rm=TRUE))
```

## Vector Arithmetic
it is unfair to draw conclusion that California has the highest incidence of murders, in this case, need to do vector calculation, so called vector arithmetic
```{r}
murders$state[which.max(murders$population)]
```

```{r}
str(murders)
```

```{r}
murder_rate<- murders$total/murders$population*100000
mean(murder_rate)
```
```{r}
murders$state[which.max(murder_rate)]
```
```{r}
murders$state[order(murder_rate, decreasing = TRUE)]
```
## Practice
```{r}
# Assign city names to `city` 
city <- c("Beijing", "Lagos", "Paris", "Rio de Janeiro", "San Juan", "Toronto")

# Store temperature values in `temp`
temp <- c(35, 88, 42, 84, 81, 30)

# Convert temperature into Celsius and overwrite the original values of 'temp' with these Celsius values
temp<- (temp - 32)*5/9
# Create a data frame `city_temps` 
city_temps<- data.frame(city, temp)
str(city_temps)
```

```{r}
# Define an object `x` with the numbers 1 through 100
x <- 1:100
# Compute the sum 
sum(1/x^2)
```

```{r}
name <- c("Mandi", "Amy", "Nicole", "Olivia")
distance <- c(0.8, 3.1, 2.8, 4.0)
time <- c(10, 30, 40, 50)
time<-time/60
time
speed<- distance/time
speed
running_test<- data.frame(name,speed)
str(running_test)

```

